---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---
### Impoerting libraries


```{r}
library(dplyr)


```

### Read tag data

```{r}
alltags <- read.csv("tags.csv" , sep=",", stringsAsFactors=FALSE)
books_tags <- read.csv("book_tags.csv" , sep=",", stringsAsFactors=FALSE)

```


there is a huge tags in the tags.csv file. many of them unuseful so I will  remove unnecessary tags. By reading the file books_tags. then order the data with respect to tags count. At last, Pick the tags count less than specific number (i.e 50). Remove this lists from tags file.


```{r}
tags <- books_tags %>% filter(books_tags$count >= 1000 )


```

### Filter the tags file with books

```{r}

mydata <- Reduce(intersect, list(books_tags$tag_id,tags$tag_id))

length(mydata) # numer of 

```
### check number of books with specified tags
make sure tags cover all books

```{r}

nrow(books_tags[books_tags$tag_id %in% mydata,]) 
x <-((books_tags[books_tags$tag_id %in% mydata,])) 
x <- unique(x$goodreads_book_id)  

length(x)

```

### view the top tags
```{r}
id <- vector(mode="numeric", length=0)
name <- vector(mode="character", length=0)

for (i in 1:length(mydata))
{
  for (j in 1:nrow(alltags))
  {
    if (mydata[i] == alltags$tag_id[j])
      {
         id[i]  <- mydata[i]
         name[i] <- alltags$tag_name[j]
         break
      }
  }
}

```

save tags to CSV file. you can remove whatever tags you want

```{r}

toptags <- data.frame(id = id, name = name)

write.csv(toptags,file = "toptags.csv")

```

You can remove any tags you do not need such as to-read, default.

```{r}
tag_name <- read.csv("toptags.csv" , sep=",", stringsAsFactors=FALSE)

x2 <- books_tags[books_tags$tag_id %in% tag_name$id, ]
x2$name <- 0


for (i in 1:nrow(tag_name)) # iteration for each tag
{
  for (j in 1:nrow(x2)) # book itration for all elements
  {
    
    if (tag_name$id[i] == x2$tag_id[j])
      {
        x2$name[j]  <- tag_name$name[i]
      }
  }
}



```

At last, linking tags to books, I save 5 tags for each book
```{r}

books <- read.csv("books.csv" , sep=",", stringsAsFactors=FALSE)
books$tag <- 0
books$tag2 <- 0
books$tag3 <- 0
books$tag4 <- 0
books$tag5 <- 0


for (i in 1:nrow(x2)) # itreation for all tags in the books
{
  for (j in 1:nrow(books)) # itreation books
  {
    if (books$goodreads_book_id[j] == x3$goodreads_book_id[i])
      {
        if  (length(x2$goodreads_book_id[x2$goodreads_book_id == 1]) > 5)
          {
           books$tag[j]   <- x2$name[i] 
           books$tag2[j]  <- x2$name[i+1] 
           books$tag3[j]  <- x2$name[i+2] 
           books$tag4[j]  <- x2$name[i+3] 
           books$tag5[j]  <- x2$name[i+4] 
          }
        else 
        {
          books$tag[j]   <- x2$name[i] 
        }
         
         
      }
  }
}

write.csv(books,file = "new2.csv")


```

